---
title: "Exploratory"
author: "Daniel Resende"
date: "November 25, 2015"
output: html_document
runtime: shiny
---
```{r libraries, echo=FALSE}
source('source.R')
```
This is the first try to build a Machine Learning algorithm to discover handwriting digits.


```{r, echo=FALSE}
inputPanel(
    sliderInput("char", label = "Select char: ",
                min = 0, max = 9, value = sample(0:9, 1), step = 1)
)

renderPlot({
    file <- "data/train.csv"
    train <- read.csv(file, nrows=1000)
    plotSample(train, n=16, char=input$char)
})
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package="shiny"),
  options=list(
    width="100%", height=550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



